High Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogenous Catalysis in Higly Sensitive Microreactors

### 2012-03-17 paper.tex
Started new figure and included two figures in the manuscript
Started on the results section

@@

\section{Test system}
Ammonia oxidation

>>>>

In Figure \ref{fig:untreated_data} an example spectrum of a methanol and atmospheric air mixture is shown. Here both the high resolution is demonstrated by the resolved methanol and molecular which has a mass difference of 43\,milliamu.
\begin{figure}
 \includegraphics[width=16cm]{untreated_data.png}%
 \caption{Raw data acquired from the TOF-MS in a gas mixture of methanol and atmospheric air. Subfigures show the three different regions of the spectrum. From the first subfigure a delay of the approximately 150\,ns can be seen which is due to delays in cables and rise time of the pulser. From the center subfigure it is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system. From the last subfigure the a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
\end{figure}

@@

\subsubsection{Data treatment}
\begin{figure}
 \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
 \caption{Example of Gaussion fit to a double peak. Each gaussion yields the area of the respective component.\label{fig:gaussian_fit}}%
\end{figure}

\section{Oxidation of ammonia}
To demonstrate the system capability ammonia oxidation on platinum thin films have been used as a test reaction. In a stoichiometric mixture of ammonia and molecular oxygen a clean combustion to molecular nitrogen and water is expected.
\begin{equation}
4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
\end{equation}
This system is, however, difficult to monitor by a QMS due to the overlap of NH$_3$ which is a reactant and OH$^-$ which is a cracking product from H$_2$O which is a product. Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at approximately m/q = 17. The mass resolution of a QMS is typically not adequate to separate the two contributions. Often a mass without cracking from either products or residue gas in the system is necessary to be able to detect the amount of ammonia in the system. Typically m/q=15 or m/q=8.5 is chosen to detect ammonia. The monitoring of other than the primary mass to charge ratio due to mass overlap is generally not wanted due to the lowering of the signal to noise ratio. This in turns affect the detection limit of the given mass. Due
